Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2019-01-03 notebook/presentation/GMSE_presentation.Rmd
Update presentation

---
title: "GMSE: a general tool for management strategy evaluation"
subtitle: "https://bradduthie.shinyapps.io/GMSE_presentation/#1"
author: "Brad Duthie (@bradduthie)"
date: "19 September 2017"
output: 
  ioslides_presentation:
    logo: Confoobio-stacked-logo.png
    css: slide.css
    widescreen: no
    fig_width: 5
    fig_height: 5
runtime: shiny
---

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Computer Image: [Markley Boyer](https://www.facebook.com/markley.boyer), Photo Image: [Robert Clark](http://www.nationalgeographic.com/contributors/c/photographer-robert-clark/)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [National Geographic](http://ngm.nationalgeographic.com/2009/09/manhattan/miller-text), [The Welikia Project](https://welikia.org/)

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Image: [Janet Tench](https://commons.wikimedia.org/wiki/File:Norfolk_potato_field_-_geograph.org.uk_-_180521.jpg)

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Kehoe et al. (2017) *Nat. Ecol. Evol.* **1**:1129–1135](https://www.nature.com/articles/s41559-017-0234-3)

@@

# Uncertainty and conservation conflict

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Bunnefeld et al. (2011) *Trends. Ecol. Evol.* **26**:441-447](https://doi.org/10.1016/j.tree.2011.05.003)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Chadès et al. (2017) *Theor. Ecol.* **10**:1-10](https://doi.org/10.1007/s12080-016-0313-0)

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Bunnefeld et al. (2011) *Trends. Ecol. Evol.* **26**:441-447](https://doi.org/10.1016/j.tree.2011.05.003)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Chadès et al. (2017) *Theor. Ecol.* **10**:1-10](https://doi.org/10.1007/s12080-016-0313-0)

@@

>>>>

---
title: "Generalised Management Strategy Evaluation: modelling biodiversity and food security"
subtitle: "https://bradduthie.shinyapps.io/GMSE_presentation/#1"
author: "Brad Duthie (@bradduthie), Jeremy Cusack, Sarobidy Rakotonarivo, and Nils Bunnefeld"
date: "8 January 2018"
output: 
  ioslides_presentation:
    logo: Confoobio-stacked-logo.png
    css: slide.css
    widescreen: no
    fig_width: 5
    fig_height: 5
runtime: shiny
---

<style type="text/css">
body p {
  color: #000000;
}
ul {
  color: black;
}
ol {
  color: black;
}
a {
    color: darkblue;
    text-decoration: none
}
.fifty {
   font-size: 50%;
   }
.seventy {
   font-size: 70%;
   }
slides > slide.backdrop {
  background: none !important;
  background-color: white !important;
}
slides > slide.title-slide hgroup h1 {
  color: black;
}
slides > slide.title-slide p {
  color: black;
}
slides > slide.light > hgroup h2 {
  color: black;
}
slides > slide.light > hgroup h1 {
  color: black;
}
ul {
  color: black;
}
ol {
  color: black;
}
p {
  color: black
}
h1, h2, h3, h4, h5, h6, h7, h8, p {
    color: black;
}
.checkbox-inline, .radio-inline {
    margin-right: 90px;
}
footer:after {
  content: attr(label);
  font-size: 12pt;
  position: absolute;
  bottom: 20px;
  left: 60px;
  line-height: 1.9;
}
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
  margin-left: 50px
}
.forceBreak { -webkit-column-break-after: always; break-after: column; }
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
<script>
$(document).ready(function() {
  $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

  $('footnote').each(function(index) {
    var text  = $(this).html();
    var fnNum = (index+1).toString();
    $(this).html(fnNum.sup());

    var footnote   = fnNum + '. ' + text + '<br/>';
    var oldContent = $(this).parents('slide').children('div.footnotes').html();
    var newContent = oldContent + footnote;
    $(this).parents('slide').children('div.footnotes').html(newContent);
  });
});
</script>

@@

Beyond Mannahatta<footnote>[Markley Boyer](https://www.facebook.com/markley.boyer), [Robert Clark](http://www.nationalgeographic.com/contributors/c/photographer-robert-clark/), [National Geographic](http://ngm.nationalgeographic.com/2009/09/manhattan/miller-text), [The Welikia Project](https://welikia.org/)</footnote>

@@

@@

Norfolk potato field<footnote>[Janet Tench](https://commons.wikimedia.org/wiki/File:Norfolk_potato_field_-_geograph.org.uk_-_180521.jpg)</footnote>

@@

@@

Potential biodiversity loss due to increased agricultural development<footnote>[Kehoe et al. (2017) *Nat. Ecol. Evol.* **1**:1129–1135](https://www.nature.com/articles/s41559-017-0234-3)</footnote>

@@

@@

# Modelling biodiversity dynamics and human decision-making

@@

**Management Strategy Evaluation**

@@

@@

**Management Strategy Evaluation**<footnote>[Bunnefeld et al. (2011) *Trends. Ecol. Evol.* **26**:441-447](https://doi.org/10.1016/j.tree.2011.05.003)</footnote><sup>,</sup><footnote>[Chadès et al. (2017) *Theor. Ecol.* **10**:1-10](https://doi.org/10.1007/s12080-016-0313-0)</footnote>

@@

## Generalised Management Strategy Evaluation (GMSE) software

- **Model biodiversity dynamics & realistic human decision-making**
- **Predict resource & land-use changes in social-ecological systems**
- **Integrate flexibly with existing ecological models**<footnote>Duthie AB, et al. (2018) Method. Ecol. Evol. [**9**:2396-2401](https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210X.13091) </footnote>
- **Open-source on [CRAN](https://cran.r-project.org/package=GMSE) and [GitHub](https://github.com/ConFooBio/gmse)**<footnote>[http://confoobio.github.io/gmse](http://confoobio.github.io/gmse)</footnote>

<p class="forceBreak"></p>

![](GMSE_Logo_Goose_300.png)

[![](http://www.r-pkg.org/badges/version/GMSE?color=yellowgreen)](https://cran.r-project.org/package=GMSE) [![](http://cranlogs.r-pkg.org/badges/grand-total/GMSE?color=yellowgreen)](http://cranlogs.r-pkg.org/badges/grand-total/GMSE)

## GMSE: population modelling (defaults)

<div class = "columns-2"><br><br>

- **Default models individual-based (IBM)**
- **Spatially explicit landscape**
- **Individual birth, movement, death**
- **Can be over-ridden with custom models**

<p class="forceBreak"></p>
<br><br>
<center>

![](GMSE_Logo_Goose_300.png)

[![](http://www.r-pkg.org/badges/version/GMSE?color=yellowgreen)](https://cran.r-project.org/package=GMSE) [![](http://cranlogs.r-pkg.org/badges/grand-total/GMSE?color=yellowgreen)](http://cranlogs.r-pkg.org/badges/grand-total/GMSE)

![](case_studies.png)

Modelling population dynamics<footnote>Cusack, JJ, et al. *Conserv. Lett.* (In press). DOI: <a ref = "https://onlinelibrary.wiley.com/doi/full/10.1111/conl.12450">10.1111/conl.12450</a>.</footnote><sup>,</sup><footnote>Cusack, JJ, et al. *In revision*</footnote>

@@

![](funding.png)

<!---
